%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 2.0 (6/7/2019)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Authors:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{article} % Default document font size

\input{structure.tex} % Include the file specifying the document structure and styling

% Set PDF meta-information
\hypersetup{
	pdftitle={Johannes Karl - Curriculum vitae},
	pdfauthor={Johannes Karl}
}
\usepackage{hanging}
%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION
%----------------------------------------------------------------------------------------

{\LARGE\bfseries Johannes Alfons Karl} % Name
\bigskip\bigskip\medskip % Whitespace

School of Psychology\\ % Address
Victoria University of Wellington 

Phone: 0226759032\\ % Phone number
\medskip % Whitespace

Email: \href{mailto:johannes.karl@vuw.ac.nz}{johannes.karl@vuw.ac.nz}\\ % Email address
Website: \href{johannes-karl.com}{johannes-karl.com}

Orcid: \href{https://orcid.org/0000-0001-5166-0728}{0000-0001-5166-0728}\\ % Academic/personal website

\vspace{0.06\textheight} % Whitespace between contact information and specific CV information


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section*{Education}

\years{2018-2021}\textsc{PhD} in Psychology, Victoria University of Wellington\\
\years{2016-2018}\textsc{Msc} in Cross-Cultural Psychology, Victoria University of Wellington\\
\years{2012-2015}\textsc{B.A} in Business Psychology, FhaM

%----------------------------------------------------------------------------------------
%	PUBLICATIONS AND TALKS
%----------------------------------------------------------------------------------------

\section*{Publications \& Talks}

\subsection*{Journal articles in print}

\begin{hangparas}{2em}{1}

\years{2021}

\textbf{Karl, J. A.},  Fischer, R., \& Jose, P. (2020). The Development of Mindfulness in Young Adults: the Relationship of Personality, Reinforcement Sensitivity, and Mindfulness \emph{Mindfulness}. doi: 10.1007/s12671-020-01576-3 \href{https://osf.io/8kufq/}{Preregistration and Materials}

\years{2020}  

Fischer, R., Bortolini, T., \textbf{Karl, J. A.} , Zilberberg, M., Robinson, K., Rabelo, A. L. A., … Mattos, P. (2020, April 22). Rapid review and meta-meta-analysis of self-guided interventions to address anxiety, depression and stress during COVID-19 social distancing. \emph{Frontiers in Psychology}. doi: 10.3389/fpsyg.2020.563876 \href{https://osf.io/fpx4s/}{Open Materials} 

\textbf{Karl, J. A.} \& Fischer, R. (2020). Revisiting the five-facet structure of mindfulness, \emph{ Measurement Instruments for the Social Sciences}. doi: 10.1186/s42409-020-00014-3 \href{https://osf.io/k2m35/}{Open Materials} 

Fischer, R., Luczak-Roesch, M., Grener, A., \textbf{Karl, J. A.}, \& Fetvadjiev, Velichko (2020). Tracing Personality Structure in Narratives: A Computational Bottom-Up Approach to Unpack Writers, Characters, and Personality in Historical Context. \emph{European Journal of Personality}.

Singh, P., Tewari, S., Kesberg, R., \textbf{Karl, J. A.}, Bulbulia, J., \&   Fischer, R. (2020). Time investments in rituals are associated with social   bonding, affect and subjective health: A longitudinal study of Diwali in two   Indian communities. \emph{Philosophical Transactions B.}

Fischer, R., \& \textbf{Karl, J. A.} (2020). The network architecture of individual differences: Personality, reward-sensitivity, and values. \emph{Personality and Individual Differences}. doi: 10.1016/j.paid.2020.109922 \href{https://osf.io/wf26d/?view_only=e1e7e704b447406bbafafa755d090513}{Open Materials} 

\textbf{Karl, J. A.}, Méndez Prado, S. M., Gračanin, A., Verhaeghen, P., Ramos, A., Mandal, S. P., Michalak, J., Zhang, C.-Q., Schmidt, C., Tran, U. S., Druica, E., Solem, S., Astani, A., Liu, X., Luciano, J. V., Tkalčić, M., Lilja, J. L., Dundas, I., Wong, S. Y., \& Fischer, R. (2020). The cross-cultural validity of the Five-Facet Mindfulness Questionnaire across 16 countries. \emph{Mindfulness}. doi: 10.1007/s12671-020-01333-6 \href{ https://osf.io/nftxb/}{Preregistration and Materials}

Ward, C., Kim, I., \textbf{Karl, J. A.}, Epstein, S., \& Park, H,-J. (2020). How normative multiculturalism relates to immigrant wellbeing. \emph{Cultural Diversity and Ethnic Minority Psychology}. doi:10.1037/cdp0000317 \href{https://osf.io/qz8jb/}{Open Materials} 

Ward, C., Watters, S. M., Stuart, J., & \textbf{Karl, J. A.}. (2020). Normative multiculturalism in socio-political context. In S. Safdar, C. Kwantes, & W. Friedlmeier (Eds.), \emph{Wiser world with multiculturalism: Proceedings from the 24th Congress of the International Association for Cross-Cultural Psychology}. https://scholarworks.gvsu.edu/iaccp_papers/281

\years{2019}
Ko, A., Pick, C. M., Kwon, J. Y., Barlev, M., Krems, J. A., Varnum, M. E. W., Neel, R., Peysha, M., Boonyasiriwat, W., Brandstätter, E., Crispim, A. C., Cruz, J. E., David, D., David, O. A., de Felipe, R. P., Fetvadjiev, V. H., Fischer, R., Galdi, S., Galindo, O., … Kenrick, D. T. (2019). Family Matters: Rethinking the Psychology of Human Social Motivation. \emph{Perspectives on Psychological Science}. doi:10.1177/1745691619872986

Chrystal, M., \textbf{Karl, J. A.}, \& Fischer, R. (2019). Mind the Gap: How discrepancies between values and behaviour affect well-being. \emph{Frontiers in Psychology}, 10:736. doi:10.3389/fpsyg.2019.00736. \href{https://osf.io/t8evu/}{Preregistration} 

Fischer, R., \& \textbf{Karl, J. A.} (2019). A primer to (cross-cultural) multi-group invariance testing possibilities in R. \emph{Frontiers in Psychology}, 10, 1507. https://doi.org/10.3389/fpsyg.2019.01507 \href{https://osf.io/agr5e/}{Open Materials} 

\textbf{Karl, J. A.}, Walsh, A., Robinson, K., Twitchin S. (2019). Developing the credibility of psychological science: Graduate student reflections on open science , \emph{Psychology Aotearoa}, 46-29

\years{2018}
\textbf{Karl, J. A.} , Fischer, R. (2018). Rituals, Repetitiveness and Cognitive Load. \emph{Human Nature}, 1–24. doi:10.1007/s12110-018-9325-3 \href{https://osf.io/rsu9x/}{Preregistration} \\
\end{hangparas}
%------------------------------------------------

\subsection*{Book Chapter}
\begin{hangparas}{2em}{1}
\years{2020} Fischer, R., \& \textbf{Karl, J. A.} (2020). Experimental Methods in Cross-Cultural Management. In B. Szkudlarek, L. Romani, D. V. Caprar, \& J. S. Osland (Eds.), The SAGE Handbook of Contemporary Cross-Cultural Management. SAGE. \\
\end{hangparas}
%------------------------------------------------

\subsection*{Articles in Review}

\begin{hangparas}{2em}{1}
\years{2020} 

Fischer, R., \textbf{Karl, J. A.} (2020). Predicting behavioral intentions to prevent or mitigate COVID-19: A cross-cultural meta-analysis of attitudes, norms and perceived behavioral control effect \emph{Social Psychological and Personality Science}. \href{https://osf.io/tsxr2/}{Preprint and Materials}

\textbf{Karl, J. A.}, Fischer, R., Elena Druică, Fabio Musso, Anastasia Cosma (2020). Testing the effectiveness of the Health Belief Model in predicting preventive behavior during the COVID-19 Pandemic. The case of Romania and Italy \emph{Frontiers in Psychology}. \href{https://osf.io/k93dr/}{Open Materials}

Bulbulia, J. A., Piven, S. D., Shaver, J. H., Mogan, R., \textbf{Karl, J. A.}, Kesberg, R., Richardson, A., Singh, P., Tewari, S., \& Fischer, R. (2020). Kiwi Diwali: A Longitudinal Investigation of Perceived Social Connection Following a Civic Religious Ritual. \emph{Human Nature}.



\end{hangparas}

\subsection*{Preprints}

\begin{hangparas}{2em}{1}
\years{2020}  

\textbf{Karl, J. A.}, \& Fischer, R. (2019). Individual difference predictors of mindfulness. \emph{PsyArXiv}.
doi:10.31234/osf.io/z2cx6

Fischer, R., \textbf{Karl, J. A.} (2020). Norms Across Cultures: A Cross-Cultural Meta-Analysis of Norms Effects in the Theory of Planned Behavior. \emph{PsyArXiv}. https://10.31234/osf.io/v2wz6

\textbf{Karl, J. A.}, & Fischer, R. (2020, April 17). Stoicism and Wellbeing. doi: 10.31234/osf.io/6rtny \href{https://osf.io/bkqgs/?view_only=0bdc04bf606b41b9a1ac4ba0c7658990}{Preregistration} 

\end{hangparas}


\subsection*{Articles in Preparation}

\begin{hangparas}{2em}{1}
\years{2020}  

Fischer, R. \&  \textbf{Karl, J. A.} (2020). Do we act on our values? - An experimental examination of the link between values, personality and behavioral choices. \href{https://osf.io/nz8ak/?view_only=b9110537370444d98d2b22dcf5f0774e}{Preregistration Study 1} | \href{https://osf.io/4juxx/?view_only=a4f0b53183824c56a90310497195d2d7}{Preregistration Study 2}

\textbf{Karl, J. A.} \& Fischer, R. (2020). Approaches to the good life: The relationship between mindfulness and stoic ideology and their relationship to personal values. 

\end{hangparas}

\subsection*{Talks}

\begin{hangparas}{2em}{1}

\years{2019}
\textbf{Karl, J. A.}, Fischer, R. (April, 2019). Rituals, Repetitiveness and Cognitive Load: A Competitive Test of Ritual Benefits for Stress. 46th Annual Conference of the Australasian Society for Experimental Psychology, Wellington, New Zealand. \href{https://osf.io/d2vgs/?view_only=672c064ce9f64c729734c33404b0e95c}{Slides}


Luczak-Roesch, M., Grener A., \textbf{Karl, J. A.}, Fetvadjiev, V. H., Fischer, R. (April, 2019). Tracing values and personality in historical narratives using a computational approach 3rd World Conference on Personality, Hanoi, Vietnam.

\textbf{Karl, J. A.}, Fetvadjiev, V.H. (April, 2019). Person–culture fit and well-being 3rd World Conference on Personality, Hanoi, Vietnam.
\href{https://osf.io/jqr35/?view_only=b30caac7fc904903b91e7faeeafa0841}{Slides}

\textbf{Karl, J. A.}, McNamara A. R (February, 2019). Gender and Morality. Poster presented at the Society of Personality and Social Psychology Conference 2019. Portland, Oregon, USA \href{https://osf.io/5xgda/?view_only=1fa31b2b2ccf4ca7a4acb75ff0f7856b}{Poster}

\years{2018}
Fischer, R., \textbf{Karl, J. A.}, Van Rensburg G. (September, 2018). Culture and well-being: A critical examination of predictors of psychological health and well-being 3rd International Conference on Well-Being and Public Policy, Wellington, New Zealand.

\textbf{Karl, J. A.}, Fischer, R. (September, 2018). Landscape and Well-Being: Using Psychology to Inform Urban Planning 3rd International Conference on Well-Being and Public Policy, Wellington, New Zealand. \href{https://osf.io/yvpq3/?view_only=1486c420e77d49e4a552796f745787b7}{Slides}

Chrystal, M., \textbf{Karl, J. A.}, Fischer, R. (March, 2018). Mind the Gap: How Discrepancies Between Values and Behaviour Affect Well-Being. Conference of the Society of Australasian Social Psychologists 2018, Wellington, New Zealand.

\years{2017}
Qumseya, T., Gonzalez, J., \textbf{Karl, J. A.}, Wiium, N. (September, 2017). Internal and External Developmental Assets Among Arab Palestinian Youth in Palestinian Territory. 18. European Conference on Developmental Psychology, Utrecht, Netherlands.

\textbf{Karl, J. A.}, Milfont, T. L. (August, 2017). Values and environmentalism: A cross-cultural meta-analysis across 58 countries. Conference of the International Conference on Environmental Psychology, A Coruña, Spain.\href{https://osf.io/nqu9j/?view_only=2965f88b9aed43df9aa2318f112475f1}{Slides}

\textbf{Karl, J. A.}, Ward, C., Masgoret, A. (August, 2017). Domestic Students’ Attitudes Toward and Willingness to Help
International Students. 12. Biennial Conference of the Asian Association of Social Psychology, Auckland, New Zealand. \href{https://osf.io/6p52f/?view_only=0e7a21100916477a8927b55e045d2ec1}{Slides}

Ward, C., Stuart, J., \textbf{Karl, J. A.} (August, 2017). Does Multiculturalism threaten Social Cohesion? 12th Biennial Conference of the Asian Association of Social Psychology, Auckland, New Zealand. 

\textbf{Karl, J. A.}, Fetvadjiev, V. H., Dimitrova, R., Ward, C., Buzea, C., Jordanov, V., Jordanov E. (July, 2017). Diversity as a Predictor of Identity and Well-being. In Under-represented ethnic and cultural groups from the Eastern-European context: A research incubator for young academics. Symposium conducted at the 9th European International Association of Cross-Cultural Psychology Conference, Warsaw, Poland. \href{https://osf.io/wcgpy/?view_only=370e5921cd2f44748e18b4d194630675}{Slides}


\textbf{Karl, J. A.}, Ward, C., Masgoret, A. (June, 2017). Public Perceptions of International Students: An Integrated Threat Approach. 10. Biennial Conference of the International Academy for Intercultural Research, New York, USA. \href{https://osf.io/a7vum/?view_only=84e3457be84e4c5180aeb5968059d061}{Slides}



Milfont, T. L., \textbf{Karl, J. A.}, Sibley, C. G. (April, 2017). Values and environmentalism: A one-year longitudinal analysis. Conference of the Society of Australasian Social Psychologists 2017, Melbourne, Australia.

\years{2016}

\textbf{Karl, J. A.}, Fetvadjiev, V. H., Dimitrova, R., Ward, C., Buzea, C., Jordanov, V., Jordanov E. (December,2016). National and Supranational Identities as Predictors of Well-being in Romania and Bulgaria. Australian Conference on Personality and Individual Differences 2016, Melbourne, Australia. \href{https://osf.io/78hx2/?view_only=529e2c2e9f12481794bd17cd2a13cec6}{Slides}

\years{2015}
\textbf{Karl, J. A.} (September, 2015). Gamification and Employee Education. Herbstkongress des Muenchner Bildungs Forums, Munich, Germany\\

\end{hangparas}
%----------------------------------------------------------------------------------------
%	TEACHING
%----------------------------------------------------------------------------------------

\section*{Teaching}

\years{2020}

\textbf{PSYC317} | Evolutionary Psychology, School of Psychology VUW
\begin{itemize}
\item Created course materials (videos, slides). \href{https://osf.io/ytnuk/}{ For examples see.}
\item Ran in person lectures/tutorials.
\item Created and marked assessment items. 

\end{itemize}

\textbf{PSYC461} | Structural Equation Modelling, School of Psychology VUW
\begin{itemize}
\item Created course materials (videos, slides, code) used to teach R.
\item Taught structural equation modelling in R to honours students.
\item Created and marked assessment items. 

\end{itemize}

\years{2019}

\textbf{INFO281} | Data Analytics Project, School of Information Management VUW
\begin{itemize}
\item Taught data analysis with R to marketing, business, and computer science students. 
\item Co-developed the structure of the course. 
\item Created teaching materials and lecture videos.
\end{itemize}

\textbf{PSYC461} | Structural Equation Modelling, School of Psychology VUW
\begin{itemize}
\item Taught structural equation modelling in SPSS and AMOS to honours students.
\item Created and marked assessment items. 
\item Created and delivered lectures aimed at transferring the skills learnt in AMOS to R.
\end{itemize}

\textbf{PSYC434} | Research Across Cultures, School of Psychology VUW
\begin{itemize}
\item Delivered four guest lectures on theoretical and practical approaches to research across cultures.
\end{itemize}

\textbf{PSYC325} | Advanced Research Methods in Psychology, School of Psychology VUW
\begin{itemize}
\item Running weekly tutorials for undergraduate students, aimed to convey concepts and skills on mediation and moderation.
\end{itemize}

\years{2018}

\textbf{PSYC317} | Evolutionary Psychology, School of Psychology VUW
\begin{itemize}
\item Running weekly tutorials for undergraduate students, aimed to convey the basics of evolutionary thinking in psychology.
\end{itemize}
%------------------------------------------------

\section*{Supervision}
\years{2019}

\textbf{Chrystal M.} | The Consequences of not Acting on Personally and Socially Important Value-Expressive Behaviours on Hedonic and Eudaimonic Wellbeing. \emph{Msc Thesis}
\begin{itemize}
\item Supported the student during data analysis and write-up of the research.
\end{itemize}


\years{2018}

\textbf{Kunz, D.} | Personality, Lifestyle, and Physiology. \emph{Bsc hons Thesis}
\begin{itemize}
\item Trained the student in collecting physiological data during a event-sampling study.
\item Supported the analysis and interpretation of the event-sampling data.
\end{itemize}

\textbf{Wainwright, T.} | Implicit Motives and Explicit Personality: Investigating the Relationships between Conscious and
Sub-Consciousness Personality. \emph{Bsc hons Thesis} \href{https://osf.io/zcsw9/?view_only=b92b80efe48a4cacabdeca94dfc07779}{Preregistration}

\begin{itemize}
\item Supported the student during preregistration, study design, data collection, and data analysis. 
\end{itemize}


\textbf{Carswell K.} | People perception: The evolution of contextual colour discriminations and intrasexual competition.  \emph{Bsc hons Thesis}
\begin{itemize}
\item Supported the student during the analysis of the data.
\end{itemize}

\textbf{Chrystal M.} | The Complexities of "Minding the Gap": Perceived Discrepancies Between Values and Behavior Affect Well-Being. \emph{Bsc hons Thesis}
\begin{itemize}
\item Supported the student in study design, data collection, analysis, and write-up for publication. 

\end{itemize}



\section*{Work Experience}
\years{current}

\textbf{Research Assistant} | Dr. Christian Schott, VUW Tourism
\begin{itemize}
\item Consulting on the psychological aspects (savouring, well-being) of tourists experiences.
\item Preparing data, analysis plan, and results for publication.
\end{itemize}

\textbf{Research and Commercialisation Assistant} | VICLink, 2019-current 


\begin{itemize}
\item Analysing and writing up existing data to create a commercial test of cultural personality.
\end{itemize}

\textbf{Lab-manager} | Mindcultureevolution Lab, 2017-current
\begin{itemize}
\item Creating and administering the lab website.
\item Organizing records, materials, and experimental devices.

\end{itemize}

\years{2019}

\textbf{Research Assistant} | Dr. Adam Grener, VUW English Literature

\begin{itemize}
\item Supporting a research project on narrative descriptions of characters in novels by Charles Dickens and Jane Austen. 
\end{itemize}

\years{2018}

\textbf{Research Assistant} | Prof. Ronald Fischer, 2017-2018

\begin{itemize}
\item Participated in a number of research projects centered around the structure of individual differences.
\end{itemize}

\years{2017}

\textbf{Research Assistant} | Prof Colleen Ward
\begin{itemize}
\item Collected and analysed data on immigrants well-being and acculturation.
\end{itemize}

\textbf{Research Assistant} |Dr. Taciano Milfont
\begin{itemize}
\item Created websites for lab and conference outreach, promoting environmental psychology.

\end{itemize}

\section*{Grants, honours \& awards}

\years{2018} 
Graduate Travel Award from the Society for Personality and Social Psychology
Faculty Strategic Research Grant from Victoria University of Wellington

\years{2017}
Faculty Strategic Research Grant from Victoria University of Wellington
Travel Award from the International Academy for Intercultural Research\\



\section*{Service to the profession}
\years{2019} 
Ethics Reviewer, VUW School of Psychology Human Ethics Committee 

Ad-hoc Reviewer for a number of Journals \href{https://publons.com/researcher/1682095/johannes-a-karl/}{Publons Profile}

\section*{References}
\textbf{Prof. Ronald Fischer} | Victoria University of Wellington

Phone: +64 04 4635153 

Email: \href{mailto:ronald.fischer@vuw.ac.nz}{ronald.fischer@vuw.ac.nz}


\textbf{AProf.  Markus Luczak-Roesch} | Victoria University of Wellington

Phone: +64 04 4635878 

Email: \href{mailto:markus.luczak-roesch@vuw.ac.nz}{markus.luczak-roesch@vuw.ac.nz}


\vfill % Whitespace before final footer

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	GRANTS, HONOURS AND AWARDS
%----------------------------------------------------------------------------------------


\end{document}
